\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule{} \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://markisherwood.me/}{\Large Mark Isherwood}} & Email: \href{mailto:mark@markisherwood.me}{mark@markisherwood.me}\\
  \href{https://markisherwood.me/}{https://markisherwood.me} & Mobile: +61 409 538 515 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart{}

    \resumeSubheading{Wunderman-Bienalto}{Melbourne, Victoria}
      {Senior Developer}{Nov 2014 --- Present}
      \resumeItemListStart{}
        \resumeItem{Drupal}
          {Worked on and build a number of different Drupal 7 and 8 websites. Experienced in custom module development, site building and architecture, custom search implementation (via Apache Solr), GovCMS and multiple Acquia products.}
        \resumeItem{Microsoft Dynamics}
          {Setup multiple instances on Microsoft Dynamics 365 for different projects. Including custom back-end services via OData API.}
        \resumeItem{Adobe Target}
          {Developed countless experiences through Adobe Target for multiple clients. Oversaw project to track users between multiple brands to better profile and target users for different experiences.}
        \resumeItem{Devops}
          {Helped start and build a multi-purpose Gulp based build system for use on a wide variety of projects. Integrated a wide number of common build tasks (SASS/Babel/Testing) into a single common project which could be used for almost any project.}
        \resumeItem{Accessibility}
          {Worked with several clients with a focus on accessibility requirements. Built and reviewed pages to ensure sites/pages met WCAG AA accessibility guidelines.}
        \resumeItem{Team Leadership}
          {Team Lead for the Melbourne development team. Handling scheduling for team on a weekly basis. Mentoring newer developers.}
      \resumeItemListEnd{}

    \resumeSubheading{cohealth}{Collingwood, Victoria}
      {System Administrator}{Jun 2014 --- Nov 2014}
      \resumeItemListStart{}
        \resumeItem{Windows Server Administrator}
          {Worked maintaining an existing Windows based server environment for several health care offices.}
        \resumeItem{Thin Client Support}
          {Provided support for Citrix based thin clients across several office locations.}
        \resumeItem{Email and phone support}
          {Handled email and phone support for several different health care sites handling issues as required.}
      \resumeItemListEnd{}

    \resumeSubheading{Swinburne University}{Glenferrie, Victoria}
      {Web Officer}{June 2012 --- June 2014}
      \resumeItemListStart{}
        \resumeItem{Custom PHP/MySQL Development}
          {Worked as sole maintainer of the online enrolment system for the university. Continued development of the of the system to expand functionality as required.}
      \resumeItemListEnd{}
  \resumeSubHeadingListEnd{}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart{}
    \resumeSubheading{Swinburne University of Technology}{Glenferrie, Victoria}
      {Bachelor of Science (Professional Software Development); Distinction average}{2011 --- Dec. 2014}
    \resumeSubheading{Swinburne University of Technology}{Glenferrie, Australia}
      {Diploma of Software Development and Website Development; Distinction average}{2008 --- 2010}
  \resumeSubHeadingListEnd{}


%-----------CERTIFICATIONS-----------------
\section{Certifications}
  \resumeSubHeadingListStart{}
    \resumeSubheading{Acquia Certified Developer --- Drupal 7}{Sep 2015}
      {}{}
    \resumeSubheading{Microsoft Certified Professional}{Sep 2017}{}{}
    \resumeSubheading{Microsoft Dynamics CRM 2016 Customisation and Configuration}{Sep 2017}{}{}
  \resumeSubHeadingListEnd{}


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart{}
   \item{
     \textbf{Languages}{: HTML, CSS, SASS, EMCAScript, jQuery, C\#, Java, PHP, SQL}
   }
   \item{
     \textbf{Technologies}{: AWS, Azure, Drupal, Node, Gulp, Yarn, Adobe Target, Apache Solr}
   }
 \resumeSubHeadingListEnd{}


%-------------------------------------------
\end{document}
